---
title: "Data Visualization Workshop: Activity 1"
output: html_document
date: 28 May 2025
---

## Part a
Type in code that will load the tidyverse, which contains ggplot2.
```{r}

```

## Part b
We are going to use the starwars data set that was loaded with the tidyverse. Take a moment to get familiar with the data set.
```{r}
?starwars
```

## Part c
Run this code below and comment what it creates. It actually does create something even if it is not very impressive.
```{r}
ggplot(starwars)
```


## Part d
Now run this code and comment on what it does. 
```{r}
ggplot(starwars, aes(x = height))
```


## Part e
Now run this code and comment on what it does. 
```{r}
ggplot(starwars, aes(x = height, y = mass))
```


## Part f
Now run this code and comment on what it does. 
```{r}
ggplot(starwars, aes(x = height, y = mass)) +
  geom_point()
```


## Part g
Hurray! We've made our first ggplot! However, there is one very obvious outlier. The outlier is from row 16. Remove row 16 and save the new data frame as `starwars2`. Remember you can remove a point by using brackets `[]` and putting a negative number in there.
```{r}

```

## Part h
Now, let's make it prettier. In the geom_bar() function, use the color option to change the color of the points to one of your choice (except don't choose black).
```{r}
ggplot(starwars2, aes(x = height, y = mass)) +
  geom_point(color = "") # Put your favorite color between the quotes.
```

## Part i
Adding onto this, let's change the shape. You can put numbers in the shape argument. Experiment with a few of these and then choose one you like (that is not a filled circle).
```{r}
ggplot(starwars2, aes(x = height, y = mass)) +
  geom_point(shape = ) # Put a number or a keyboard symbol (in quotes) after the =
```

## Part j
Let's change the x and y labels now. For the x-axis, change the label to "Height (cm)" and change the y-axis label to "Mass (kg)"
```{r}
ggplot(starwars2, aes(x = height, y = mass)) +
  geom_point() +
  labs() # Change the x and y axis labels
```

## Part k
Now copy and paste the code from part j and add a title. You can do this by either putting `title =` in the `labs()` function or adding on the `ggtitle()` function. 
```{r}

```

## Part l
It is time to change the font size. In the follow code, copy and paste the code from part k so that it has the proper labels and title. Then, the way this is set up, the text size for the axis labels will be increased to size 14. Change also the text size for the title to size 18.
```{r}
ggplot(starwars2, aes(x = height, y = mass)) +
  geom_point() +
  # Put labs() function here. Put a + after it 
  #   so the theme function gets added on
  theme(axis.title = element_text(size = 14))
```

## Part m
Finally, copy and paste your plot from part l. Go ahead and add the line of best fit to this plot with geom_smooth(method = "lm"). By default, confidence interval bands will also be shown. You can remove them using se = FALSE. Feel free to change the color of the line as well.  
```{r}

```

